R code for 'Apparent physiological costs of blood parasite infection in the early-life of a vertebrate host - only in highest infections

### 2022-03-30 MS_physiology_infection.Rmd
Add files via upload

## Table 4 
## ----------------------------------------------------------------------------- 
sjPlot::tab_model(
  lmer_br_para,
  lmer_bt_para,
  lmer_bc_para,
  lmer_gr_para,
  show.ci50 = T ,
  show.stat = T,
  string.stat = "t",
  p.val = "kr",
  show.df = T,
  dv.labels = c("Breathing rate","Body temperature","\U0394 Body condition","Growth rate"),
  file = "./Tables/Table4_results_parasitemia_lmer_physiological_parameters_p.val_kr.html")
```

>>>>

## Table 2 
## ----------------------------------------------------------------------------- 
sjPlot::tab_model(
  lmer_br_para,
  lmer_bt_para,
  lmer_bc_para,
  lmer_gr_para,
  show.ci50 = T ,
  show.stat = T,
  string.stat = "t",
  p.val = "kr",
  show.df = T,
  dv.labels = c("Breathing rate","Body temperature","\U0394 Body condition","Growth rate"),
  file = "./Tables/Table2_results_parasitemia_lmer_physiological_parameters_p.val_kr.html")
```
